%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%-------------------------------------------------------------------------------
%   PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%-------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

% Document margins
\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.3in]{geometry}
\usepackage{hyperref}

\name{Wesley Wei} % Your name
% \address{新竹市科學園路107向8號5樓之1} % Your address
\address{40 Lower Campus Rd, Latin Way F272} % Your address
%(optional)
% Your phone number and email address
\address{(617)-275-9957 \\
    \href{mailto:Wesley.Wei@Tufts.edu}{Wesley.Wei@Tufts.edu} \\
GitHub: \href{https://github.com/946336}{946336}}

\begin{document}

%-------------------------------------------------------------------------------
%   WORK EXPERIENCE SECTION
%-------------------------------------------------------------------------------

% Resume section for work experience, etc
\begin{rSection}{Experience}

% Subsection for each entry
% \begin{rSubsection}{Employer, location, etc}{Date(s)}{Job title}
% \item TEXT
% \end{rSubsection}

\begin{rSubsection}{Tufts University, Medford, MA}{September 2015 -
    Present}{Teaching Assistant - Department of Computer Science}

\item Developed strong communication skills while providing guidance to
    students regarding program architecture and core programming concepts.

\end{rSubsection}

\begin{rSubsection}{NSRRC, Hsinchu, Taiwan}{June 2016 - August 2016}{Temporary
    Assistant}

\item Added the capability to operate on a subset of available data, greatly
    speeding up processing of regions of interest within larger data sets.

\item Resolved technical debt in an existing image preprocessing PyQt
    application with the goal of easing future development.

\end{rSubsection}

\begin{rSubsection}{NTHU, Hsinchu, Taiwan}{June 2015 - November
    2015}{Temporary Assistant}

\item Automated analysis of data for an optical tweezers lab using MATLAB,
    reducing processing times from 20 minutes to a few seconds per data set.

\end{rSubsection}

% \smallskip
\bigskip

\end{rSection}

%-------------------------------------------------------------------------------
%   TECHNICAL STRENGTHS SECTION
%-------------------------------------------------------------------------------

\begin{rSection}{Technical Strengths}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Programming Languages & C, C++, Python, Bash/Shell, MATLAB, \\
    & HTML/CSS/Javascript, Java \\
Technologies \& Tools & GNU/Linux, Git, Qt, Django, Android \\
\end{tabular}

% \smallskip
\bigskip
\end{rSection}

%-------------------------------------------------------------------------------
%   EDUCATION SECTION
%-------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf Tufts University, Medford, MA} \hfill {Expected May 2018} \\
Bachelor of Science, Computer Science
% Bachelor of Science, Mathematics (Expected) \\
% GPA 3.29/4.0 \smallskip
% {\em {\bf \em Relevant coursework}: Data Structures, Machine Structure \&
% Assembly, Programming Languages, Algorithms, Advanced Functional Programming,
% Operating Systems, Machine Learning, Computer Graphics, Computational Theory,
% Programming Language Design.}
% \smallskip

\smallskip
\bigskip
\end{rSection}

%-------------------------------------------------------------------------------
%   OTHER ACTIVITIES
%-------------------------------------------------------------------------------

\begin{rSection}{Projects}

\begin{rSubsection} {\href{https://www.cap-tal.com} {Cap-Tal}}
    {Summer 2017 - Present}{}

\item Built a simple website for a small, loose development team under the name
    Cap-Tal.

\end{rSubsection}

\begin{rSubsection}{\href {https://www.questionablebattleship.com/}{Questionable
    Battleship}}{Summer 2017 - Present}{Cap-Tal}

\item Led the development of a Battleship game and proposed future extensions to
    enable on-the-fly rule tweaking.

\item Designed and developed the backend server application for the game and the
    Websocket protocol.

\end{rSubsection}

\begin{rSubsection}{\href{http://2016.polyhack.tufts.io/}{Polyhack at
    Tufts}}{October 2016}{Team Snapsassin (Second Place)}

\item Worked with a team to develop an Android game using a face-recognition
    API to identify players of the game

\item Implemented requests to the RESTful facial recognition API, and the
    interpretation of the results.

% \item Android application to automate moderation of the game Assassin, using a
%     face recognition API to confirm “kills.”
\end{rSubsection}

\begin{rSubsection}{\href{https://idhack16.devpost.com/}{ID Hack at
    Tufts}}{March 2016}{Team HandSPASMS (Qualcomm Award)}

\item Worked with a team to develop an Android application to enable doctors
    to easily remind patients of upcoming appointments via SMS

\item Diagnosed HTTP request handling errors in the application

\end{rSubsection}
\end{rSection}

% \begin{rSection}{Other Activities}

% \begin{rSubsection}{Proofreading Academic Manuscripts}{2010 - Present}{}
% \item Proofread various articles for researchers from NSRRC and NTHU
% \end{rSubsection}

% \smallskip
% % \bigskip
% \end{rSection}

%-------------------------------------------------------------------------------
%   EXAMPLE SECTION
%-------------------------------------------------------------------------------

%\begin{rSection}{Section Name}

%Section content\ldots

%\end{rSection}

%-------------------------------------------------------------------------------

\end{document}

